Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
rollback change in CFP *quotation* to original

\begin{quote}
In practice, scientific software activities are part of an ecosystem where key roles are held by 
developers, users, and funders. All three groups supply resources to the ecosystem, as well as 
requirements that bound it. Roughly following the example of NSF's Vision and Strategy for Software 
\footnote{\url{http://www.nsf.gov/publications/pub_summ.jsp?ods_key=nsf12113}}~\cite{NSF_software_vision}, 
the ecosystem may be viewed as having challenges related to:

>>>>

\begin{quote}
In practice, scientific software activities are part of an ecosystem where key roles are held by 
developers, users, and funders. All three groups supply resources to the ecosystem, as well as 
requirements that bound it. Roughly following the example of NSF's Vision and Strategy for Software 
(\url{http://www.nsf.gov/publications/pub_summ.jsp?ods_key=nsf12113})~\cite{NSF_software_vision}, 
the ecosystem may be viewed as having challenges related to:
